[Re] Marriage and happiness: Providing evidence against a relationship between inequality and happiness in Oishi, Kesebir, and Diener (2011)

### 2020-02-20 analysis/paper.Rmd
Adds read in for table 1 R script

``` {r setup, echo = FALSE, message = FALSE, warnings = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures")
#knitr::read_chunk("src/my-external-code.R")

@@

>>>>

``` {r setup, echo = FALSE, message = FALSE, warnings = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures")

knitr::read_chunk("001-creates-table-1.R")
knitr::read_chunk("002-creates-table-2.R")

@@

```{r import-and-clean-the-data-for-table-1, eval=TRUE}
```

```{r create-the-correlations-and-table, eval=TRUE}
```

```{r display-table-1, eval=TRUE, results='asis'}
```
